### 2018-09-12 chapter-latex/related-work.tex
chapter is the version Kees sent to the editor

A number of answers to Lipman's question have been proposed, but as we have argued elsewhere, it appears that some of these do not to hold up to scrutiny \citep{van2009utility,vanDeemterBook}. For example,
%
\begin{itemize}
\item It has been proposed that the existence of vague words makes a language more efficient \citep{barwiseperry}. The idea is that vagueness allows the use of one and the same word (e.g., ``big'') in different situations, which require different standards. For instance, the vague word ``big'' can denote a mouse a well as an elephant. The idea is plausible, but the problem is that ``big" is efficient not because it is vague (i.e., not because it allows borderline cases) but because it is context dependent. To see this, note for example that superlatives are not vague, but they {\em are} context dependent: ``the biggest $x$" ascribes different sizes to the referent depending on $x$. It is for this reason that we can use the word ``biggest''  to talk about the biggest mouse, the biggest elephant, and so on. Context-dependence, however, does not imply vagueness.
%
\item It has been pointed out that vague words are capable of combining a statement of quantity (along some dimension) with an evaluative statement \citep{veltman}. The idea is that when we say ``The patient has a fever'', we do not merely assert that her temperature lies above a certain value, we also imply that the deviation is large enough to be clinically significant (i.e., something is not right with the patient). The problem with this plausible idea is that evaluation does not imply vagueness. For example, the medical term ``obese'' is evaluative (i.e., it is not healthy to be obese), yet its standard medical definition in terms of Body Mass Index is perfectly crisp, with BMI values above 30 counting as obese.
\end{itemize}
%
Analogous observations can be made about a number of other purported benefits of vagueness; one of the few hypotheses left standing at the moment is the {\em cost reduction} hypothesis, which we mentioned in the previous section. The findings on which we are reporting in the present paper will follow a familiar pattern: we will explore the cost reduction hypothesis, only to conclude that it does not stand up to scrutiny. Our approach, this time, will be experimental: we conduct controlled experiments to investigate the effect that vague expressions have on a hearer.

>>>>

A number of answers to Lipman's question have been proposed, but as we have argued elsewhere, it appears that some of these do not to hold up to scrutiny \citep{van2009utility,vanDeemterBook}. For example,
%
\begin{itemize}
\item It has been proposed that the existence of vague words makes a language more efficient \citep{barwiseperry}. The idea is that vagueness allows the use of one and the same word (e.g., ``big'') in different situations, which require different standards. For instance, the vague word ``big'' can denote a mouse a well as an elephant. The idea is plausible, but the problem is that ``big" is efficient not because it is vague (i.e., not because it allows borderline cases) but because it is context dependent. To see this, note for example that superlatives are not vague (i.e., they do not permit borderline cases), but they {\em are} context dependent: ``the biggest $x$" ascribes different sizes to the referent depending on $x$. It is for this reason that we can use the word ``biggest''  to talk about the biggest mouse, the biggest elephant, and so on. Context-dependence, however, does not imply vagueness.
%
\item Vague words are capable of combining a statement of quantity with an evaluative statement \citep{veltman}. The idea is that when we say ``The patient has a fever'', we do not merely assert that her temperature lies above a certain value, we also imply that the deviation is clinically significant (i.e., something is not right with the patient). The problem with this plausible idea is that evaluation does not imply vagueness. For example, the medical term ``obese'' is evaluative (i.e., it is not healthy to be obese), yet its standard medical definition in terms of Body Mass Index is perfectly crisp (i.e., without borderline cases), with all and only BMI values above 30 counting as obese.
\end{itemize}
%
Analogous observations can be made about a number of other purported benefits of vagueness; one of the few hypotheses left standing at the moment is the {\em cost reduction} hypothesis, which we mentioned in the previous section. The findings on which we are reporting in the present paper will follow a familiar pattern: we will explore the cost reduction hypothesis, only to conclude that it may not stand up to scrutiny. Our approach, this time, will be experimental: we conduct controlled experiments to investigate the effect that vague expressions have on a hearer.
